Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-09-13 batchdedup/2012concl.tex

\section{Conclusion}
\label{sect:final}
In this paper we propose a multi-level selective deduplication scheme for 
snapshot service in VM cloud. 
Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
while cross-VM deduplication with a small common data set
effectively  covers a large amount of duplicated data.
Our solution accomplishes the majority of
potential global deduplication saving while still meets stringent cloud resources requirement. 
Evaluation using real user's VM data shows
our solution can accomplish 75\% of what complete global
deduplication can do. 
Compare to today's widely-used snapshot technique, our scheme reduces almost
two-third of snapshot storage cost.
Finally, our scheme uses a very small amount of memory on each node, and leaves
room for additional optimization we are further studying.
\section*{Acknowledgments}
{
We would like to thank Weicai Chen and Shikun Tian from Alibaba for their kind support, 
and the anonymous referees for their comments.
Wei Zhang has received internship support from Alibaba  for VM backup system development.
This work was supported in part by NSF IIS-1118106.
Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and
do not necessarily reflect the views of Alibaba or the National Science Foundation.
}
%Noted that 6\% is still significant, which is about 24GB per each VM and for a 1000 node Aliyun cluster,
%this is about 600 terabytes.

>>>>

\section{Conclusion}
\label{sect:final}
In this paper we propose a multi-level selective deduplication scheme for 
snapshot service in VM cloud. 
Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
while cross-VM deduplication with a small common data set
effectively  covers a large amount of duplicated data.
Our solution accomplishes the majority of
potential global deduplication saving while still meets stringent cloud resources requirement. 
Evaluation using real user's VM data shows
our solution can accomplish 75\% of what complete global
deduplication can do. 
Compare to today's widely-used snapshot technique, our scheme reduces almost
two-third of snapshot storage cost.
Finally, our scheme uses a very small amount of memory on each node, and leaves
room for additional optimization we are further studying.
%\section*{Acknowledgments}
%{
%We would like to thank Weicai Chen and Shikun Tian from Alibaba for their kind support, 
%and the anonymous referees for their comments.
%Wei Zhang has received internship support from Alibaba  for VM backup system development.
%This work was supported in part by NSF IIS-1118106.
%Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and
%do not necessarily reflect the views of Alibaba or the National Science Foundation.
%}
%Noted that 6\% is still significant, which is about 24GB per each VM and for a 1000 node Aliyun cluster,
%this is about 600 terabytes.

### 2013-09-13 batchdedup/analysis.tex
updated performance model
Started round scheduling section

\section{ Old Performance Analysis and Comparison}
\label{sect:analysis-old}

@@

The total disk requirement  per machine for hosting the global index  and meta  data of  accumulated requests is:
\[
x*r *k*u*(1-d2) + r*u.
\]
That is not so big, and is acceptable as we show later.

\section{New Performance Analysis and Comparison}
\label{sect:analysis}

\begin{table}[ht]
\centering
\begin{tabular}{|p{1.25cm}|p{6.5cm}|}
\hline
$p$ &  the number of machines in the cluster\\ 
\hline
$v$ & the number of VMs per machine. At Alibaba, $v=25$\\
\hline
$x$ & is the number of snapshots saved for each VM. At Alibaba, $x=10$\\
\hline
%$k$ & the number of iterations to complete all virtual machine backup. Each iteration performs v/k backups.\\
%\hline
$t$ & the amount of temporary disk space used per machine for deduplication\\
\hline
$m$ & the amount of memory used per machine for deduplication. Our goal is to minimize this\\
\hline
$s$ & the average size of virtual machine image. At Alibaba, from our collected data, $s=40GB$\\
\hline
$d_1$ & the average  deduplication ratio using segment-based dirty-bit. $d_1=77\%$\\
\hline
$d_2$ & the average  deduplication ratio using content chunk fingerprints after segment-based deduplication. For Alaba dataset tested,  $d_2=50$\%\\
\hline
$d_3$ & the average number of dup-with-new blocks, as a fraction of $r$ (defined below)\\
\hline
$b_r$ & the average disk bandwidth for reading from local storage at each machine\\
\hline
$b_w$ & the average disk bandwidth for writing to local storage at each machine\\
\hline
$b_b$ & average write bandwidth to back-end storage (block store)\\
\hline
$q$ & the number of buckets to accumulate requests at each machine. (total number of buckets is $p*q$)\\
\hline
$c$ & the chunk block size in bytes.  In practice $c=4KB$\\
\hline
$u$ & the record size of detection request per block.  In practice, $u$=40. That includes block ID and fingerprint\\
\hline
$e$ & the size of a duplicate summary record for each chunk block\\
\hline
$m_n$ & the memory allocated to network send \& receive buffering. Total network memory is $2m_n$, wich each buffer of size $m_n/p$\\
\hline
%$m$ & the maximum memory allocated for deduplication purpose.  A $g$ fraction used for machine-machine network  request buffering and $(1-g)$ fraction used for memory-disk bucket buffering\\
%\hline
$\alpha_n$ & the latency for sending a message in a cluster\\
\hline
%$\alpha_d$ disk latency\\
%\hline
$\beta$ & time cost for in-memory duplicate comparison\\
\hline
\end{tabular}
\caption{Modeling  parameters and symbols.}
\label{tab:symbol}
\end{table}

@@

Here we develop a model for the total backup time, which becomes important in
trying to minimize the CoW cost during backup \emph{CoW should be explained and
justified before this point in the paper}.  The backup process can be broken
into 4 stages, where each stage has two parts, first an all-to-all exchange of
data, then local processing to prepare for the next stage.

In Stage 1a, the dirty segments are read from the virtual disk, the hash of
each block is computed, and dedup requests are sent to the machine hosting the
blocks' respective partitions. Due to the synchronization in each stage, Stage
1a needs to wait for the most heavily loaded machine to read all it's data - so
the read stage depends on $r_{max}$, while the write stage, which is balanced
by the hash partitioning, depends on $r$. We first read $r$ blocks from disk,
send $r$ dedup requests, and then save the received requests to temporary files
(one for each parition). The time for the first stage can be expressed as:
\[
    r_{max} c / b_r + \alpha_n\frac{p u r_{max}}{m_n} + r u / b_w
\]

In Stage 1b, each partition index is read from disk, then the dedup requests
(from Stage 1a) for that paritition are processed and the results are written
back out to disk. The results are broken into 3 groups: duplicate blocks, new
blocks, and dup-with-new blocks, which are duplicates of blocks that are new to
this batch.

@@

In Stage 2a the new block results from Stage 1 are sent to the requesters, and
in Stage 2b the new blocks are written out to the storage system. We will now
mostly be dealing with the $r(1-d_2)$ blocks that are new to the system (or
$r_{max}(1-d_2)$ when we must wait for the most heavily loaded machine). In 2b
the dedup results must be read and the actual disk blocks for each new block
must be re-read before they can be sent to the block store. To avoid seeking
we have found it faster to simply re-read all the dirty data and ignore the
duplicate blocks rather than find only the new blocks on disk. The CoW locking
on the filesystem cannot end until after the dirty data is re-read in Stage 2b.

The cost of Stage 2a is:
\[
    r(1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d2) p}{m_n} + r_{max}(1-d_2)e / b_w
\]
and the cost of Stage 2b is:
\[
    r_{max}c / b_r + r_{max}(1-d_2)e / b_r + r(1-d_2)c / b_b
\]

After the new blocks have been written to the block store, and references to
them have been obtained, those references must be returned to the parition
index holder so that those blocks may be deduped in the future (and also so
dup-with-new requests can be handled in this run). This Stage 3a, to read the
new index entries, return them to the parition index holder, and save the
received references, costs:
\[
    r_{max} (1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d_2) p}{m_n} + r(1-d_2)e / b_w
\]

Stage 3b consists of updating the partition index with the new block references
from Stage 3a, and also updating the dup-with-new results from Stage 1. First
we load the new references from Stage 2b into memory, and then dedup the
dup-with-new requests against the new block references. Once the dup-with-new
results have chunk references, we can add the dup-with-new results to the
duplicate result files. We then add the new references to the corresponding
partition index to handle future dedup requests. Stage 3b costs:
\[
    r ((1-d_2) + d_3)e/b_r + r (1-d_2)\beta + r((1-d_2) + d_3)e / b_w
\]

In the final stage (Stage 4), all duplicate references (including the
dup-with-new references from 3b) are returned to the requesters, so that the
snapshot recipes may be updated with references to those blocks. This process
costs:
\[
    r d_2 e / b_r + \alpha_n\frac{e r_{max} d_2 p}{m_n} + r e / b_w
\]

@@

\subsection{A Comparison with Other Approaches}

The memory  space requirement for the data domain approach with bloom filter is:
\[
x*r k u (1-d2)/r
\]
where $r$ is the bloom filter with about  1:10 ratio in practice.  The disk space used  is 
\[
x*r *k *u*(1-d_2).
\]

>>>>

\comments{
\section{ Old Performance Analysis and Comparison}
\label{sect:analysis-old}

@@

The total disk requirement  per machine for hosting the global index  and meta  data of  accumulated requests is:
\[
x*r *k*u*(1-d2) + r*u.
\]
That is not so big, and is acceptable as we show later.
}

\section{Performance Analysis and Comparison}
\label{sect:analysis}

\begin{table}[ht]
\centering
\begin{tabular}{|p{0.50cm}|p{7cm}|}
\hline
$p$ &  the number of machines in the cluster\\ 
\hline
$v$ & the number of VMs per machine. At Alibaba, $v=25$\\
\hline
$x$ & is the number of snapshots saved for each VM. At Alibaba, $x=10$\\
\hline
%$k$ & the number of iterations to complete all virtual machine backup. Each iteration performs v/k backups.\\
%\hline
$t$ & the amount of temporary disk space used per machine for deduplication\\
\hline
$m$ & the amount of memory used per machine for deduplication. Our goal is to minimize this\\
\hline
$s$ & the average size of virtual machine image. At Alibaba, from our collected data, $s=40GB$\\
\hline
$d_1$ & the average  deduplication ratio using segment-based dirty-bit. $d_1=77\%$\\
\hline
$d_2$ & the average  deduplication ratio using content chunk fingerprints after segment-based deduplication. For Alaba dataset tested,  $d_2=50$\%\\
\hline
$d_3$ & the average number of dup-with-new blocks, as a fraction of $r$ (defined below)\\
\hline
$b_r$ & the average disk bandwidth for reading from local storage at each machine\\
\hline
$b_w$ & the average disk bandwidth for writing to local storage at each machine\\
\hline
$b_b$ & average write bandwidth to back-end storage (block store)\\
\hline
$q$ & the number of buckets to accumulate requests at each machine. (total number of buckets is $p*q$)\\
\hline
$c$ & the chunk block size in bytes.  In practice $c=4KB$\\
\hline
$u$ & the record size of detection request per block.  In practice, $u$=40. That includes block ID and fingerprint\\
\hline
$e$ & the size of a duplicate summary record for each chunk block\\
\hline
$m_n$ & the memory allocated to network send \& receive buffering. Total network memory is $2m_n$, wich each buffer of size $m_n/p$\\
\hline
%$m$ & the maximum memory allocated for deduplication purpose.  A $g$ fraction used for machine-machine network  request buffering and $(1-g)$ fraction used for memory-disk bucket buffering\\
%\hline
$\alpha_n$ & the latency for sending a message in a cluster\\
\hline
%$\alpha_d$ disk latency\\
%\hline
$\beta$ & time cost for in-memory duplicate comparison\\
\hline
\end{tabular}
\caption{Modeling  parameters and symbols.}
\label{tab:symbol}
\end{table}

Here we develop a model for the total backup time, which becomes important in
trying to minimize the CoW cost during backup \emph{CoW should be explained and
justified before this point in the paper}.  The backup process can be broken
into 4 stages, where the first 3 stages each have two parts, first an
all-to-all exchange of
data, then local processing to prepare for the next stage.

@@

In Stage 1a, the dirty segments are read from the virtual disk, the hash of
each block is computed, and dedup requests are sent to the machine hosting the
blocks' respective partitions. Due to the synchronization in each stage, Stage
1a needs to wait for the most heavily loaded machine to read all it's data - so
the read stage depends on $r_{max}$, while the write stage, which is balanced
by the hash partitioning, depends on $r$. We first read $r$ blocks from disk,
send $r$ dedup requests, and then save the received requests to temporary files
(one for each parition). The time for the first stage can be expressed as:
\[
    r_{max} c / b_r + \alpha_n\frac{u r_{max}}{m_n} + r u / b_w
\]

In Stage 1b, each partition index is read from disk, then the dedup requests
(from Stage 1a) for that paritition are processed and the dedup results are
written
back out to disk. The results are broken into 3 groups for each partition:
duplicate blocks, new
blocks, and dup-with-new blocks, which are duplicates of blocks that are new to
this batch.

@@

In Stage 2a the new block results from Stage 1 are sent to the requesters, and
in Stage 2b the new blocks are written out to the storage system. We will now
mostly be dealing with the $r(1-d_2)$ blocks that are new to the system (or
$r_{max}(1-d_2)$ when we must wait for the most heavily loaded machine). In 2b
the dedup new block results must be read and the actual disk blocks for each
new block
must be re-read before they can be sent to the block store. To avoid seeking
we have found it faster to simply re-read all the dirty data and ignore the
duplicate blocks rather than find only the new blocks on disk. The CoW locking
on the filesystem cannot end until after the dirty data is re-read in Stage 2b.

The cost of Stage 2a is:
\[
    r(1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d2)}{m_n} + r_{max}(1-d_2)e / b_w
\]
and the cost of Stage 2b is:
\[
    r_{max}c / b_r + r_{max}(1-d_2)e / b_r% + r_{max}(1-d_2)c / b_b
\]

After the new blocks have been written to the block store, and references to
them have been obtained, those references must be returned to the parition
index holder so that those blocks may be deduped in the future (and also so
dup-with-new requests can be handled in this round). This Stage 3a, to read the
new index entries, return them to the parition index holder, and save the
received references, costs:
\[
    r_{max} (1-d_2)e / b_r + \alpha_n\frac{e r_{max}(1-d_2)}{m_n} + r(1-d_2)e / b_w
\]

Stage 3b consists of updating the partition index with the new block references
from Stage 3a, and also updating the dup-with-new results from Stage 1. First
we load the new references from Stage 2b into memory, and then dedup the
dup-with-new requests against the new block references. Once the dup-with-new
results have chunk references, we can add the dup-with-new results to the
duplicate result files initially created in 1b. We then add the new references
to the corresponding
partition indices to handle future dedup requests. Stage 3b costs:
\[
    r ((1-d_2) + d_3)e/b_r + r d_3\beta + r((1-d_2) + d_3)e / b_w
\]

In the final stage (Stage 4), all duplicate references (including the
dup-with-new references from 3b) are returned to the requesters, so that the
snapshot recipes may be updated with references to those blocks. This process
costs:
\[
    r d_2 e / b_r + \alpha_n\frac{e r_{max} d_2}{m_n} + r e / b_w
\]

@@

\subsection{A Comparison with Other Approaches}
\comments{
The memory  space requirement for the data domain approach with bloom filter is:
\[
x*r k u (1-d2)/r
\]
where $r$ is the bloom filter with about  1:10 ratio in practice.  The disk space used  is 
\[
x*r *k *u*(1-d_2).
\]
}

### 2013-09-13 batchdedup/arch.tex
updated architecture
updated architecture and scheduling. updated and split data flow figure into stages.

\begin{figure*}[tbhp]
\centering

\includegraphics[width=0.95\textwidth]{steps.pdf}
\caption{Processing flow of Stage  1 (dirty segment scan and request accumulation), Stage 2 
(fingerprint comparison and summary output),  and Stage 3 (non-duplicate block backup).}
\label{fig:flow}
\end{figure*}

%\subsection{Processing flow and resource usage}
The data flow of our multi-stage duplicate detection is depicted in Figure~\ref{fig:flow}. 
%let $v$ be the total number of virtual machines hosted in  a cluster,  
%we divide the backup into $k$  iterations. 
%\begin{itemize}
%\item
In Stage 1a, each machine independently reads  
%$v/k$  
VM images that need a backup
and forms duplicate  detection requests. 
%For those dirty segments,
%segments that have been modified since last backup indicated by dirty bits,  
The system divides  each dirty segment into a sequence of chunk blocks,  computes the meta 
information such as chunk fingerprints,  sends a request to a proper machine, and accumulates  
received requests into a partition on the local temporary disk storage. 
The partition mapping uses a hash function applied to the content fingerprint. 
Assuming all machines have a  homogeneous resource configuration, each machine is evenly  assigned with
$q$ partitions of global index and it accumulates corresponding requests on the disk. 
There are two options to allocate buffers at each machine. 
1) Each machine has  $p\times q$ send buffers corresponding to $p\times q$ partitions in the cluster
since a content block in a VM image of this machine can be sent to any of these partitions.
2) Each machine allocates $p$ send buffers to deliver requests to $p$ machines; it allocates 
$p$ receive buffers to collect requests  from other machines.
Then the system copies requests from each of $p$ receive buffers to  $q$ local request buffers,
and outputs each request buffer to one of the request partitions on the disk
when this request buffer becomes full.  Option 2, which is  depicted in Figure~\ref{fig:flow},
is much more efficient than Option 1 because $2p+q$ is much smaller than
$p\times q$, except for the very small  values. 
As a result, each buffer in Option 2 has a bigger size to accumulate requests and that means
less disk seek overhead.

@@

@@

@@

In the final Stage of our algorithm, Stage 4, All duplicate references,
including dup-with-new blocks, are returned to the requesters and the snapshot
recipes are updated with those pointers.

The above steps can be executed by each machine using one thread to minimize
the use of computing resources.
The  disk storage usage on each machine 
is fairly small for  storing part of the global index and
accumulating  duplicate detection requests that contain fingerprint information.   
We impose a memory limit $M$ allocated for each stage of processing at each machine.
The usage of $M$ is controlled as follows and space allocation among buffers is optimized based on the relative
ratio between the cross-machine network  startup cost and disk access startup cost such as seek time.
Using a bigger buffer  can mitigate the impact of slower startup cost. 
\begin{itemize}
\item For Stage 1, $M$  is divided for 
1) an I/O buffer to read dirty segments; 2) $2p$ send/receive buffers and $q$ request  buffers.

>>>>

%\begin{figure*}[tbhp]
%\centering
%\includegraphics[width=0.95\textwidth]{images/DataFlow.pdf}
%\caption{Processing flow of Stage  1 (dirty segment scan and request accumulation), Stage 2 
%(fingerprint comparison and summary output),  and Stage 3 (non-duplicate block backup).}
%\label{fig:flow}
%\end{figure*}

\begin{figure}[th]
\centering
\includegraphics[width=0.5\textwidth]{images/Stage1.pdf}
\caption{Processing flow of Stage 1.}
\label{fig:stage1}
\end{figure}

%\subsection{Processing flow and resource usage}
%The data flow of our multi-stage duplicate detection is depicted in Figure~\ref{fig:flow}. 
%\begin{itemize}
%\item
In Stage 1a, each machine independently reads  
%$v/k$  
VM images that need a backup
and forms duplicate  detection requests. 
%For those dirty segments,
%segments that have been modified since last backup indicated by dirty bits,  
The system divides  each dirty segment into a sequence of chunk blocks,  computes the meta 
information such as chunk fingerprints,  sends a request to a proper machine, and accumulates  
received requests into a partition on the local temporary disk storage. 
The partition mapping uses a hash function applied to the content fingerprint. 
Assuming all machines have a  homogeneous resource configuration, each machine is evenly  assigned with
$q$ partitions of global index and it accumulates corresponding requests on the disk. 
There are two options to allocate buffers at each machine. 
1) Each machine has  $p\times q$ send buffers corresponding to $p\times q$ partitions in the cluster
since a content block in a VM image of this machine can be sent to any of these partitions.
2) Each machine allocates $p$ send buffers to deliver requests to $p$ machines; it allocates 
$p$ receive buffers to collect requests  from other machines.
Then the system copies requests from each of $p$ receive buffers to  $q$ local request buffers,
and outputs each request buffer to one of the request partitions on the disk
when this request buffer becomes full.  Option 2, which is  depicted in Figure~\ref{fig:flow},
is much more efficient than Option 1 because $2p+q$ is much smaller than
$p\times q$, except for the very small  values. 
As a result, each buffer in Option 2 has a bigger size to accumulate requests and that means
less disk seek overhead.

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.5\textwidth]{images/Stage2.pdf}
\caption{Processing flow of Stage 2.}
\label{fig:stage2}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.5\textwidth]{images/Stage3.pdf}
\caption{Processing flow of Stage 3.}
\label{fig:stage3}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.5\textwidth]{images/Stage4.pdf}
\caption{Processing flow of Stage 4.}
\label{fig:stage4}
\end{figure}

In the final Stage of our algorithm, Stage 4, All duplicate references,
including dup-with-new blocks, are returned to the requesters from the index
holders and the snapshot
recipes are updated with those pointers.

The above steps can be executed by each machine using one thread to minimize
the use of computing resources.
The  disk storage usage on each machine 
is fairly small for  storing part of the global index and
accumulating  duplicate detection requests that contain fingerprint information.   
We impose a memory limit $M$ allocated for each stage of processing at each machine.
%The usage of $M$ is controlled as follows and space allocation among buffers is optimized based on the relative
%ratio between the cross-machine network  startup cost and disk access startup cost such as seek time.
%Using a bigger buffer  can mitigate the impact of slower startup cost. 
$M$ includes space for network communications and buffering data which is being
sent to disk. We have found that as long as the write/read buffers are not
unreasonably small (e.g. 4KB), the size of the disk buffers does not have a
great impact on backup time, so we allocate small disk buffers (e.g. 128KB read
and 2.5MB shared across all write buffers), and then allocate the remaining
memory to index space or network buffers, depending on the stage.
\begin{itemize}
\item For Stage 1, $M$ is divided for 
1) an I/O buffer to read dirty segments; 2) $2p$ send/receive buffers and $q$
disk buffers for deduplication requests.

### 2013-09-13 batchdedup/background.tex

%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
represented as virtual disk image files in the host operating system.
For VM snapshot backup, file-level semantics are normally not provided.
Snapshot operations take place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. 
%Only raw access information at disk block level are provided. 
%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
%only a very small slice of cluster resource can be used for the backup purpose.

%The previous work for storage backup has extensively used  data deduplication techniques can eliminate redundancy globally among different files from different users.
Backup systems have been developed to use content fingerprints to identify duplicate
content~\cite{venti02,Rhea2008}.
Offline deduplication is used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
%,NGmiddleware2011}.
%Today's commercial data backup systems (e.g. from EMC and NetApp)
%\cite{emc_avamar}\cite{datadomain_whitepaper}
%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
Several techniques have been proposed to speedup searching of duplicate
fingerprints. For example, the data domain method ~\cite{bottleneck08} 
uses  an in-memory Bloom filter and a prefetching cache for data blocks  which may be
accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
%Still such methods use a significant amount of memory resource for filtering and caching.
%Such methods use dedicated nodes for deduplication, which add cost to cloud infrastructure and are less scalable.
As discussed in Section~\ref{sect:intro},
there is no dedicated resource for deduplication in our targeted setting and low memory usage
 is required so that the resource impact to other cloud services is minimized.
%NG et al.~\cite{ NGmiddleware2011}  use
%a related filtering technique for integrating deduplication in Linux  file system and the memory
%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
%Lillibridge et al.~\cite{sparseindex09} break list of chunks
%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
%These are segments that share many chunk IDs with the incoming segment with high probability.
The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
%lookup  
In comparison, this paper focuses on  full deduplication without approximation.

Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}. 
All of the above approaches have focused on
such inline duplicate detection in which  deduplication of an individual block  is on the critical write path.
In our work, this constraint is relaxed and 
there is a waiting time for many duplicate detection requests. This relaxation is acceptable because 
in our context, finishing the backup of required VM images within a reasonable time window is more
important than optimizing individual VM block  backup requests.

>>>>

At a cloud cluster node providing access to multiple virtual machines, each
instance of a guest operating system runs on a virtual machine (VM), accessing
virtual hard disks represented as virtual disk image files in the host
operating system. For VM snapshot backups, file-level semantics are normally
not provided, and snapshot operations take place at the virtual device driver
level.  This meands no fine-grained file system metadata can be used to
determine the changed data.

Another issue is the sheer size of the backups. to maintain mutiple daily
uncompressed snapshots of each VM would be very expensive, even though
most of the data remains the same from day to day, and even between VMs common
software packages and operating systems mean that the amount of unique data is
much smaller. Backup systems have been developed to use content fingerprints to
identify duplicate content~\cite{venti02,Rhea2008}. Offline deduplication is
used in~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks
during idle time.  Several techniques have been proposed to speedup searching
of duplicate fingerprints. For example, the data domain method
~\cite{bottleneck08} uses  an in-memory Bloom filter and a prefetching cache
for data blocks  which may be accessed.  An improvement to this work with
parallelization is in ~\cite{MAD210,DEBAR}.  As discussed in
Section~\ref{sect:intro}, there is no dedicated resource for deduplication in
our targeted setting and low memory usage is required so that the resource
impact to other cloud services is minimized. Approximation techniques which
reduce the memory requirement at the expense of deduplication efficiency are
studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}.  In comparison, this
paper focuses on full deduplication without approximation

%%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
%At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
%represented as virtual disk image files in the host operating system.
%For VM snapshot backup, file-level semantics are normally not provided.
%Snapshot operations take place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. 
%%Only raw access information at disk block level are provided. 
%%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
%%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
%%only a very small slice of cluster resource can be used for the backup purpose.

%%The previous work for storage backup has extensively used  data deduplication techniques can eliminate redundancy globally among different files from different users.
%Backup systems have been developed to use content fingerprints to identify duplicate
%content~\cite{venti02,Rhea2008}.
%Offline deduplication is 
%used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
%%,NGmiddleware2011}.
%%Today's commercial data backup systems (e.g. from EMC and NetApp)
%%\cite{emc_avamar}\cite{datadomain_whitepaper}
%%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
%Several techniques have been proposed to speedup searching of duplicate
%fingerprints. For example, the data domain method ~\cite{bottleneck08} 
%uses  an in-memory Bloom filter and a prefetching cache for data blocks  which may be
%accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
%As discussed in Section~\ref{sect:intro},
%there is no dedicated resource for deduplication in our targeted setting and low memory usage
% is required so that the resource impact to other cloud services is minimized.
%%NG et al.~\cite{ NGmiddleware2011}  use
%%a related filtering technique for integrating deduplication in Linux  file system and the memory
%%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
%%Lillibridge et al.~\cite{sparseindex09} break list of chunks
%%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
%%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
%%These are segments that share many chunk IDs with the incoming segment with high probability.
%The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
%%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
%to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
%%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
%%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
%%lookup  
%In comparison, this paper focuses on  full deduplication without approximation.
%%We also take advantages of the fact that in a VM cloud environment,
%%the virtual device driver can easily keep track if  large data
%%segments have been modified using dirty bits and such information can avoid sending
%%unmodified data segments for deduplication, which significantly saves cost.

Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}. 
All of the above approaches have focused on
such inline duplicate detection in which  deduplication of an individual block  is on the critical write path.
In our work, this constraint is relaxed and 
there is a waiting time for many duplicate detection requests. This relaxation is acceptable because 
in our context, efficiently finishing the backup of VM images within a reasonable time window is more
important than optimizing individual VM block  backup requests, and by batch
processing the deduplication requests we can decrease resource usage.
